Specific leaf area explains difference in biomass partitioning between woody plant functional types

### 2014-10-09 manuscript/draftpaper.tex
Figures now saved in manuscript/figures and added to manuscript

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\bibliographystyle{plain}

@@

\section{Main text}

@@

\section{Lit notes}

@@

\section{Results and Discussion}

\section{Methods}

\bibliography{allometry}

>>>>

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\bibliographystyle{plain}

@@

\section{Introduction}

@@

%------------------------------------------------------------------------------------%
\section{Methods}

%------------------------------------------------------------------------------------%
\section{Results}

%------------------------------------------------------------------------------------%
\section{Discussion}

%------------------------------------------------------------------------------------%
\section{Lit notes}

@@

\cite{grier_notes:_1974} early study on leaf mass proportionality to sapwood area (and uses mass not area).

\section{Figures}

\begin{figure}[h!]
    \centering
    \includegraphics{figure1_mlf_astba2_bypft.pdf}
    \caption{Leaf mass per unit basal stem area. Each symbol is an individual plant. Lines are generalized additive model fits.}
    \label{fig:figure1}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{figure2_mlf_alf_astbaest_pftmeans.pdf}
    \caption{Average leaf mass per unit basal stem area (panel 1), and leaf area per unit basal stem area (panel 2) for the three major plant functional types. Error bars are 95\% confidence interval for the mean (calculated with a mixed-effects model with species within study as the random effect). Letters denote significant differences. }
    \label{fig:figure2}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{figure3_LMF_pft_lines.pdf}
    \caption{Leaf mass fraction (leaf mass / aboveground biomass) by plant functional type. Each symbol is an individual plant. Lines are generalized additive model fits.}
    \label{fig:figure3}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{figure4_LAR_pft_lines.pdf}
    \caption{Leaf area ratio (leaf area / aboveground biomass) by plant functional type. Each symbol is an individual plant. Lines are generalized additive model fits.}
    \label{fig:figure4}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{figure4_LAR_pft_lines.pdf}
    \caption{Leaf area ratio (leaf area / aboveground biomass) by plant functional type. Each symbol is an individual plant. Lines are generalized additive model fits.}
    \label{fig:figure4}
\end{figure}

\clearpage
\bibliography{allometry}
